Competing Bandits: \\ The Perils of Exploration under Competition

### 2019-01-29 paper/content/model.tex
updates
tweaks

Concretely, each of the two firms has a \emph{reputation score}, and each agent's choice is driven by these two numbers. We posit a version of rational behavior: each agent chooses a firm with a maximal reputation score (breaking ties uniformly). The reputation score is simply a sliding window average: an average reward of the last $M$ agents that chose this firm. \asedit{This is similar to ratings aggregators on many online platforms such as Yelp, Tripadvisor, etc.).}

@@

\asedit{\xhdr{Consistency.}}
While we experiments with various MAB instances and parameter settings, in the main paper we only report plots for selected, representative experiments. Additional plots will be published in the full version. Unless noted otherwise, our findings are based on and consistent with all these plots.

>>>>

Concretely, each of the two firms has a \emph{reputation score}, and each agent's choice is driven by these two numbers. We posit a version of rational behavior: each agent chooses a firm with a maximal reputation score (breaking ties uniformly). The reputation score is simply a sliding window average: an average reward of the last $M$ agents that chose this firm. \asedit{This is similar to ratings aggregators on many online platforms such as Yelp, Tripadvisor, etc.}

@@

\asedit{\xhdr{Consistency.}}
While we experiment with various MAB instances and parameter settings, in the main paper we only report plots for selected, representative experiments. Additional plots will be published in the full version. Unless noted otherwise, our findings are based on and consistent with all these plots.

### 2019-01-29 paper/content/perf_in_iso.tex
Some space-saving.
tweaks

\section{Algorithms' Performance in Isolation}\label{sec:isolation}

We start with a pilot experiment in which we investigate each algorithm's performance ``in isolation": in a stand-alone MAB problem without competition. We focus on reputation scores generated by each algorithm. We confirm that algorithms' performance is ordered as we'd expect:
    $\TS > \DEG > \DG$
for a sufficiently long time horizon.
For each algorithm and each MAB instance, we compute the mean reputation score at each round, averaged over all \MRVs. We plot the \emph{mean reputation trajectory}: how this score evolves over time. Figure \ref{prelim_means} shows such a plot for the Needle In Haystack instance; for other MAB instances the plots are similar. We summarize this finding as follows:

>>>>

\section{Performance in Isolation}\label{sec:isolation}

We start with a pilot experiment in which we investigate each algorithm's performance ``in isolation": in a stand-alone MAB problem without competition. We focus on reputation scores generated by each algorithm. We confirm that algorithms' performance is ordered as we'd expect:
    $\TS > \DEG > \DG$
for a sufficiently long time horizon.\footnote{For most of our experiments we report results for $T = 2000$ and this claim holds at this $T$}, 
For each algorithm and each MAB instance, we compute the mean reputation score at each round, averaged over all \MRVs. We plot the \emph{mean reputation trajectory}: how this score evolves over time. Figure \ref{prelim_means} shows such a plot for the Needle In Haystack instance; for other MAB instances the plots are similar. We summarize this finding as follows:
